### 2018-03-07 chapter2/ms.tex
Testing autoref

To help provide a framework for these observations, and to more broadly investigate the coupled issues of kilonova detectability and contaminant rejection, we present here a systematic study of the feasibility of kilonova detections and assessing the effects of a population of contaminant sources during follow-up of a GW trigger using wide-field optical telescopes. This study will guide the development of observational strategies for wide-field searches that maximize the likelihood of detecting a GW optical counterpart. The paper is organized as follows: In Section~\ref{sec:ch2_contaminants} we describe the kilonova models utilized in this work and develop the list of contaminating transients considered in this work. In Section~\ref{sec:ch2_phase} we  describe observational features that may be used to isolate kilonovae from the population of potential contaminants. In Section~\ref{sec:ch2_MCsims} we present detailed Monte Carlo simulations of observations to investigate the detectability of kilonovae and contaminant rejection for various observational strategies. In Section~\ref{sec:ch2_diff}, we address issues that arise from the possible lack of a deep pre-existing template. We then discuss the effects of modifications to the standard kilonovae models on our results in Section~\ref{sec:ch2_altkilo}. In Section~\ref{sec:ch2_disc}, we asses the expected performance of current and future wide-field telescopes in the framework of kilonova detectability and contaminant rejection and develop strategies for GW follow-up. Conclusions are presented in Section~\ref{sec:ch2_conc}.

>>>>

To help provide a framework for these observations, and to more broadly investigate the coupled issues of kilonova detectability and contaminant rejection, we present here a systematic study of the feasibility of kilonova detections and assessing the effects of a population of contaminant sources during follow-up of a GW trigger using wide-field optical telescopes. This study will guide the development of observational strategies for wide-field searches that maximize the likelihood of detecting a GW optical counterpart. The paper is organized as follows: In \autoref{sec:ch2_contaminants} we describe the kilonova models utilized in this work and develop the list of contaminating transients considered in this work. In \autoref{sec:ch2_phase} we  describe observational features that may be used to isolate kilonovae from the population of potential contaminants. In \autoref{sec:ch2_MCsims} we present detailed Monte Carlo simulations of observations to investigate the detectability of kilonovae and contaminant rejection for various observational strategies. In \autoref{sec:ch2_diff}, we address issues that arise from the possible lack of a deep pre-existing template. We then discuss the effects of modifications to the standard kilonovae models on our results in \autoref{sec:ch2_altkilo}. In \autoref{sec:ch2_disc}, we asses the expected performance of current and future wide-field telescopes in the framework of kilonova detectability and contaminant rejection and develop strategies for GW follow-up. Conclusions are presented in \autoref{sec:ch2_conc}.
